---
title: "ReproducibilityR"
author: "Richard J. Telford"
date: "January 30, 2019"
output:
  ioslides_presentation:
    widescreen: true
    css: toc-style.css
    includes:
      in_header: etc/TOC-for-IOslides-in-Rmarkdown-master/TOC_generator.js.wrapper
    self_contained: no
bibliography: etc/reproducibility.bib
csl: etc/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Route map

<!-- Link to table of content javascript 
<script language="JavaScript" src="etc/TOC-for-IOslides-in-Rmarkdown-master/ TOC_generator.js"></script>-->

<!-- Link to table of content style 
<link rel="stylesheet" type="text/css" href="etc/TOC-for-IOslides-in-Rmarkdown-master/toc-style.css">-->

<!-- add div element table of content for javascript to fill -->
<div id="toc"></div>

# Why Reproducibility? {.section}

## Why? 

"Despite extensive efforts, we were not able to reconstruct where the error occurred. It probably resulted from using erroneously an earlier version of the analysis, or an issue with file naming."

## Basic idea

- Data cleaning
- Data formatting
- Statistical analysis
- Plotting
- Putting numbers in the MS

... all done with code. All reproducible

# You need a style guide {.section}


## Why

 - Makes code easier to read
 - Makes code easier to debug

Make your own style - but be consistent


## White-space is free! 

Makes code more readable

Put spaces around all infix operators (`%>%`, `+`, `-`, `<-`, (but not `:` or `::` )) and around `=` in function calls. 

Always put a space after a comma, never before.

### Good
```{r good, eval = FALSE, echo=TRUE}
average <- mean(feet / 12 + inches, na.rm = TRUE)
```
### Bad
```{r bad, eval = FALSE, echo=TRUE}
average<-mean(feet/12+inches,na.rm=TRUE)
```

R-studio shortcut `ctrl-shift-A`

## Split long commands over multiple lines

```{r split, eval = FALSE, echo=TRUE}
list(
  total = a + b + c, 
  mean  = (a + b + c) / n
)
```

## Indentation makes code more readable

### Good
```{r indent, eval = FALSE, echo=TRUE}
pos <- function(x) {
  if (is.null(dim(x))) {
    x[x > 0]
  } else{
    x[, colSums(x) > 0, drop  = FALSE]
  }
}
```

### Bad
```{r noindent, eval = FALSE, echo=TRUE}
pos <- function(x){
if(is.null(dim(x)))
{x[x >0]} 
else{
x[, colSums(x) > 0, drop  = FALSE]
}}
```


## Comments

Use # to start comments.

Help you and others to understand what you did

Comments should explain the why, not the what.

Use comments to break up file into readable chunks for navigation
```{r comments, eval = FALSE, echo=TRUE}
#### Load data ####
...
#### Plot data ####
...
```
Also to omit code - shortcut `ctrl-shift-C`

 
## Split analyses over multiple files

Long scripts become difficult to navigate

Fix by moving parts of the code into different files

For example: 

 - data import code to "loadData.R"
 - functions to "functions.R"

Import with  
```{r imports, eval = FALSE}
source("loadData.R")
source("functions.R")
```
 
## Don't repeat yourself

Repeated code is hard to maintain

Make repeated code into functions.

```{r functions, eval = FALSE}
my_fun <- function(x, pow = 2) {x ^ pow}
my_fun(7)
```
Single place to maintain

Reuse ggplot objects or entire plots

```{r recycle, eval = FALSE}
g <- ggplot(iris, aes(x = Petal.Length, y = Sepal.Length, colour = Species))  +
  geom_point() 
g + aes(x = Petal.Width, y = Sepal.Width)
```
 
## Avoid `attach()`

Unless you love strange bugs

Very rarely useful to `attach` - many better [options](https://coderclub.b.uib.no/2016/05/03/dont-get-attached-to-attach/)
 
## Paths

Don't use absolute paths 

`c://my_files/my_project/my_file.csv`

or `setwd('c://my_files/my_project/')`

Use paths relative to rstudio project

or use `here::here()`

## Reading

Google's R Style Guide [https://google.github.io/styleguide/Rguide.xml](https://google.github.io/styleguide/Rguide.xml)

Hadley Wickham, H. Style Guide _Advanced R_
[http://adv-r.had.co.nz/Style.html](http://adv-r.had.co.nz/Style.html)

# Version control {.section}

```{r child = "versionControl.Rmd"}
``` 

# Rmarkdown {.section}

```{r child = "rmarkdown.Rmd"}
``` 

# Dependency management {.section}

```{r child = "dependencyManagement.Rmd"}
``` 

## References