---
title: "ReproducibilityR"
author: 
 name: "Richard J. Telford"
 twitter: "richardjtelford"
 company: "Dept. Biological Sciences, UiB"
date: "January 30, 2019"
output:
  ioslides_presentation:
    widescreen: true
bibliography: etc/reproducibility.bib
csl: etc/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Route map

- What do we mean by reproducibility?
- You need a style guide
- Version control
- Rmarkdown
    * Citations
    * Drake
- Dependency management


# Why Reproducibility? {.section}

## Why? 

"Despite extensive efforts, we were not able to reconstruct where the error occurred. It probably resulted from using erroneously an earlier version of the analysis, or an issue with file naming."

## Basic idea

- Data cleaning
- Data formatting
- Statistical analysis
- Plotting
- Putting numbers in the MS

... all done with code. All reproducible

# You need a style guide {.section}

```{r child = "styleguide.Rmd"}
```

# Version control {.section}

```{r child = "versionControl.Rmd"}
``` 

# Rmarkdown {.section}

```{r child = "rmarkdown.Rmd"}
``` 

# Dependency management {.section}

```{r child = "dependencyManagement.Rmd"}
``` 

## References