---
title: Adopt a Style Guide
author: "Richard J. Telford"
date: '2016-05-05'
---

```{r setup_stg, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Why

 - Makes code easier to read
 - Makes code easier to debug

Make your own style - but be consistent


## White-space is free! 

Makes code more readable

Put spaces around all infix operators (`%>%`, `+`, `-`, `<-`, (but not `:` or `::` )) and around `=` in function calls. 

Always put a space after a comma, never before.

### Good
```{r good, eval = FALSE}
average <- mean(feet / 12 + inches, na.rm = TRUE)
```
### Bad
```{r bad, eval = FALSE}
average<-mean(feet/12+inches,na.rm=TRUE)
```

R-studio shortcut `ctrl-shift-A`

## Split long commands over multiple lines

```{r split, eval = FALSE}
list(
  total = a + b + c, 
  mean  = (a + b + c) / n
)
```

## Indentation makes code more readable

### Good
```{r indent, eval = FALSE}
pos <- function(x) {
  if (is.null(dim(x))) {
    x[x > 0]
  } else{
    x[, colSums(x) > 0, drop  = FALSE]
  }
}
```

### Bad
```{r noindent, eval = FALSE}
pos <- function(x){
if(is.null(dim(x)))
{x[x >0]} 
else{
x[, colSums(x) > 0, drop  = FALSE]
}}
```


## Comments

Use # to start comments.

Help you and others to understand what you did

Comments should explain the why, not the what.

Use comments to break up file into readable chunks for navigation
```{r comments, eval = FALSE}
#### Load data ####
...
#### Plot data ####
...
```
Also to omit code - shortcut `ctrl-shift-C`

 
## Split analyses over multiple files

Long scripts become difficult to navigate

Fix by moving parts of the code into different files

For example: 

 - data import code to "loadData.R"
 - functions to "functions.R"

Import with  
```{r imports, eval = FALSE}
source("loadData.R")
source("functions.R")
```
 
## Don't repeat yourself

Repeated code is hard to maintain

Make repeated code into functions.

```{r functions, eval = FALSE}
my_fun <- function(x, pow = 2) {x ^ pow}
my_fun(7)
```
Single place to maintain

Reuse ggplot objects or entire plots

```{r recycle, eval = FALSE}
g <- ggplot(iris, aes(x = Petal.Length, y = Sepal.Length, colour = Species))  +
  geom_point() 
g + aes(x = Petal.Width, y = Sepal.Width)
```
 
## Avoid `attach()`

Unless you love strange bugs

Very rarely useful to `attach` - many better [options](https://coderclub.b.uib.no/2016/05/03/dont-get-attached-to-attach/)
 
## Paths

Don't use absolute paths 

`c://my_files/my_project/my_file.csv`

or `setwd('c://my_files/my_project/')`

Use paths relative to rstudio project

or use `here::here()`

## Reading

Google's R Style Guide [https://google.github.io/styleguide/Rguide.xml](https://google.github.io/styleguide/Rguide.xml)

Hadley Wickham, H. Style Guide _Advanced R_
[http://adv-r.had.co.nz/Style.html](http://adv-r.had.co.nz/Style.html)
